    %-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[label=\textcolor{black}{--}, leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
\AtBeginDocument{\pagecolor{white}\color{black}}
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Frederick Andrews} % Your Name
\newcommand{\course}{Computer Engineering} % Your Program
\newcommand{\roll}{xxxxxxx} % Your Roll No.
\newcommand{\phone}{873-353-3056} % Your Phone Number
\newcommand{\emaila}{Freddywandrews@gmail.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
\hyphenpenalty=10000
\exhyphenpenalty=10000

\setlength{\footskip}{5pt}


%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ +1-\phone}\\
  B.A.Sc. Computer Engineering  & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \\
  {University of Ottawa, Ontario, Canada}& \href{https://github.com/FreddyyAndrews}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {github.com/FreddyyAndrews}} \\  
& \href{https://www.linkedin.com/in/frederick-wilson-andrews/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {linkedin.com/in/frederick-wilson-andrews/}}
\end{tabularx}
}
\vspace{-8mm}

%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {B.A.Sc. Computer Engineering}{GPA: 9.22/10}
      {University of Ottawa, Ottawa Ontario, Canada}{September 2021- December 2025}
      \resumeItemListStart
      \vspace{1.0mm}
      \resumeItem{Hardware Coursework:}
          {Electronics, \textbf{VHDL} for Digital Logic Design, \textbf{MATLAB} for Signal Analysis, \textbf{FPGA}, \textbf{ARM Microcontroller} Assembly, Circuit Theory, \textbf{Quartus Prime}}
          \vspace{1.0mm}
        \resumeItem{Software Coursework:}
          {Operating Systems, \textbf{Data Structures and Algorithms}, \textbf{OOP} in \textbf{Python} and \textbf{Java}, Advanced Programming Concepts in \textbf{C++}.}
          \vspace{1.0mm}
          \resumeItem{Extracurricular:}
          {Treasurer for \textbf{IEEE} uOttawa Student Branch and \textbf{Women in Engineering} uOttawa.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-8mm}
%
%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Full-Stack Data Science Intern}{Ottawa, ON}
      {Larus Technologies}{January 2024 - Present}
      \vspace{1mm}
      \resumeItemListStart
    \item {Developed a \textbf{Machine Learning Orchestration Web App} with real-time \textbf{dashboards} and \textbf{Kubeflow pipeline triggers}, enabling parallel training of \textbf{25 models} and supporting a team of \textbf{10 data scientists and annotators}.}
    \vspace{1mm}
    \item {Designed a data \textbf{annotation} page with keyword highlighting, filtering, metric tracking, and comments, increasing annotation speed to \textbf{300 per hour} and improving productivity and data quality.}
    \vspace{1mm}
    \item {Technologies Used: \textbf{Google BigQuery, Python, Streamlit, Pandas, SQL, Kubeflow}}
    \vspace{1mm}
    \resumeItemListEnd
    
    \vspace{-3mm}

    \resumeSubheading
      {Software Developer Intern}{Ottawa, ON}
      {Canadian Center for Cyber Security}{May 2023 - August 2023}
      \vspace{1mm}
      \resumeItemListStart
    \item {Ameliorated team’s \textbf{Spark} framework monitoring by sending logs to \textbf{Azure Eventhub}. Connected logs to the \textbf{ELK stack} and used \textbf{Kibana} to display a dashboard resulting in improved monitoring of system health.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-8mm}

%-----------PROJECTS-----------------
\section{\textbf{Projects}}
\resumeSubHeadingListStart
\resumeProject
      {Edge AI Drone Object Detection and Mapping System} %Project Name
      {Drone-based object detection system with real-time GPS mapping for park rangers.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Benchmarked \textbf{edge AI} inference on \textbf{Hailo 8L accelerator} using \textbf{YOLOv8s}, increasing detection accuracy by \textbf{tiling} 4K video into 640x640 segments, improving \textbf{small-object detection} performance by over \textbf{250\%}.}
         \vspace{1.0mm}
         \item {Integrated \textbf{UART} and \textbf{SPI communication} between Raspberry Pi 5, \textbf{Quectel L76K GPS}, and \textbf{SX1262 LoRa transceiver} to transmit precise, real-time telemetry data upon object detection, enabling instant location updates in the mapping application.}
         \vspace{1.0mm}
         \item {Source Code: \href{https://github.com/FreddyyAndrews/TAILS-Embedded}{\faGithub\ github.com/FreddyyAndrews/TAILS-Embedded}}
    \resumeItemListEnd 
    \vspace{-1.5mm}
    \resumeProject
      {Pipelined RISC Processor with Hazard Detection} %Project Name
      {A structurally implemented, pipelined RISC processor with full hazard detection capabilities.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Designed and verified \textbf{gate-level} hardware implementation in \textbf{VHDL}, supporting \textbf{arithmetic} operations, \textbf{branching}, unconditional jumps, and \textbf{memory load/store} instructions.}
         \vspace{1.0mm}
        \item {Created a \textbf{hazard detection} unit from scratch, effectively handling \textbf{data and control hazards} to maintain pipeline efficiency and instruction correctness.}

    \resumeItemListEnd 
    \vspace{-1.5mm}
    \resumeProject
      {Realtime Debuggable Traffic Light Control System with UART Interface} %Project Name
      {An FPGA-based traffic management system with real-time UART debugging capability.} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item{Implemented a \textbf{state machine} in \textbf{VHDL} at the gate-level to simulate traffic conditions triggered by physical switch inputs representing vehicle presence.}
        \vspace{1mm}
        \item{Developed a \textbf{UART receiver/transmitter} interface with a \textbf{baud rate of 9600}, enabling real-time logging and debugging via terminal connection. Synthesized the design on a \textbf{Cyclone IV DE2-115 FPGA} board.}
        \vspace{1mm}
        \item {Source Code: \href{https://github.com/FreddyyAndrews/Traffic-Light-Control-System-With-UART}{\faGithub\ github.com/FreddyyAndrews/Traffic-Light-Control-System-With-UART}}
    \resumeItemListEnd
    \vspace{-1.5mm}
    \resumeProject
      {FreddyyBot Chess Engine} %Project Name
      {A chess engine designed from scratch in C++} %Project Name, Location Name
      {} %Event Dates

      \resumeItemListStart
        \item {Developed a custom move generation system with efficient board evaluation, enabling high-speed \textbf{position tree traversal} of over \textbf{300,000 nodes per second}. }
         \vspace{1.0mm}
        \item {Source Code: \href{https://github.com/FreddyyAndrews/FreddyyBot}{\faGithub\ github.com/FreddyyAndrews/FreddyyBot}}
        \vspace{1.0mm}
        \item {LiChess Profile: \href{https://lichess.org/@/FreddyyBot}{\faChessKnight\ lichess.org/@/FreddyyBot}}
    \resumeItemListEnd 
  \resumeSubHeadingListEnd
\vspace{-8mm}

%-----------Technical skills-----------------
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.05in, label={}]
    \small{
    \item{\textbf{Programming Languages:} C++, Python, Java, VHDL, Bash, SQL.}
    \vspace{-2mm}
    \item{\textbf{Certifications:} Azure AI Fundamentals.}
    \vspace{-2mm}
    \item{\textbf{Technologies:} Altera FPGA, Quartus, OpenCV, Google Cloud Platform, Azure, Kubeflow, Scikit-learn, Pandas.}
    }
\end{itemize}
 \vspace{-16pt}

\end{document}
